---
title: "HW2"
author: "Jiaying Shi"
date: "10/3/2019"
output: html_document
---
Everyone loves maps, they like to zoom to where they live, where they’ve been, and it often places valuable context about their neighborhood, country and world. Students will create a series of leaflet maps with data from polygons, polylines, dataframe (csv/xlsx) or point and/or raster data. Map data can be spatial data from any resource. (World Maps are fine)

Each Map will include:

A Basemap
One map with a layer of points(Students may use either circles or markers)
One map with a layer of lines
One map with a layer of polygons
One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
One map must contain a functioning layersControl() with two basemaps and two different layers (by name do not need to be a different type of layer)
```{r setup, include=FALSE}
require(rgdal)
require(leaflet)
require(leaflet.extras)
require(dplyr)
require(readxl)
require(stringr)
```

```{r}

```

#load Spatial Data

```{r}
permit <- read.csv("Building_Permit.csv")

river <- readOGR("National_Wild_and_Scenic_River_Segments_Feature_Layer.geojson")

```


# Map with a layer of points

```{r}
pal.b <- colorFactor(c("#E69F00", "#1A9850"), c("Non-Residential", "Residential"))

leaflet() %>%
  addProviderTiles("OpenStreetMap.HOT") %>%
  addCircleMarkers(data = permit, lng = ~Longitude, lat = ~Latitude, radius = 1,color = ~pal(PermitClassMapped)) %>%
  addLegend(position = "topright" , pal = pal.b, values = permit$PermitClassMapped , title = "Building Permit Map")
```

# Map with a layer of lines

```{r}
pal.r <- colorFactor(palette = "RdYlBu", domain = river$CLASSIFICATION)
  

leaflet(data = river) %>%
  addProviderTiles("Esri.WorldTerrain", options = providerTileOptions(noWrap = TRUE)) %>%
  addPolylines(color = "#63CBD3") %>%
  addLegend(position = "topright", pal = pal.r, values = ~CLASSIFICATION, title = "National Wild and Scenic River Segments")

```

